Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium version \YellowPaperVersionNumber}}

### 2018-03-03 Paper.tex
Add \nonumber to lines in multi-line equations in equation arrays

After the message call or contract creation is processed, the state is finalised by determining the amount to be refunded, $g^*$ from the remaining gas, $g'$, plus some allowance from the refund counter, to the sender at the original rate.
\begin{equation}
g^* \equiv g' + \min \left\{ \Big\lfloor \dfrac{T_{\mathrm{g}} - g'}{2} \Big\rfloor, \hyperlink{refund_balance_defn_words_A__r}{A_{\mathrm{r}}} \right\}
\end{equation}

@@

Throughout the present work, it is assumed that if $\boldsymbol{\sigma}_1[r]$ was originally undefined, it will be created as an account with no code or state and zero balance and nonce. Thus the previous equation should be taken to mean:
\begin{equation}
\boldsymbol{\sigma}_1 \equiv \boldsymbol{\sigma}_1' \quad \text{except:} \\
\end{equation}
\begin{equation}
\boldsymbol{\sigma}_1[s] \equiv \begin{cases}
\varnothing & \text{if}\ \boldsymbol{\sigma}_1'[s] = \varnothing \ \wedge\ v = 0 \\
\mathbf{a}_1 &\text{otherwise}
\end{cases}
\end{equation}
\begin{equation}
\mathbf{a}_1 \equiv \left(\boldsymbol{\sigma}_1'[s]_{\mathrm{n}}, \boldsymbol{\sigma}_1'[s]_{\mathrm{b}} - v, \boldsymbol{\sigma}_1'[s]_{\mathbf{s}}, \boldsymbol{\sigma}_1'[s]_{\mathrm{c}}\right)
\end{equation}
\begin{equation}
\text{and}\quad \boldsymbol{\sigma}_1' \equiv \boldsymbol{\sigma} \quad \text{except:} \\
\end{equation}
\begin{equation}
\begin{cases}
\boldsymbol{\sigma}_1'[r] \equiv (0, v, \mathtt{\tiny TRIE}(\varnothing), \mathtt{\tiny KEC}(())) & \text{if} \quad \boldsymbol{\sigma}[r] = \varnothing \wedge v \neq 0 \\
\boldsymbol{\sigma}_1'[r] \equiv \varnothing & \text{if}\quad \boldsymbol{\sigma}[r] = \varnothing \wedge v = 0 \\
\boldsymbol{\sigma}_1'[r] \equiv \mathbf{a}_1' & \text{otherwise}
\end{cases}
\end{equation}
\begin{equation}
\mathbf{a}_1' \equiv (\boldsymbol{\sigma}[r]_{\mathrm{n}}, \boldsymbol{\sigma}[r]_{\mathrm{b}} + v, \boldsymbol{\sigma}[r]_{\mathbf{s}}, \boldsymbol{\sigma}[r]_{\mathrm{c}})
\end{equation}

@@

The application of rewards to a block involves raising the balance of the accounts of the beneficiary address of the block and each ommer by a certain amount. We raise the block's beneficiary account by \hyperlink{R__block}{$R_{\mathrm{block}}$}; for each ommer, we raise the block's beneficiary by an additional $\frac{1}{32}$ of the block reward and the beneficiary of the ommer gets rewarded depending on the block number.\hypertarget{Omega}{} Formally we define the function $\Omega$:
\begin{eqnarray}
\\ \nonumber
\Omega(B, \boldsymbol{\sigma}) & \equiv & \boldsymbol{\sigma}': \boldsymbol{\sigma}' = \boldsymbol{\sigma} \quad \text{except:} \\
\qquad\boldsymbol{\sigma}'[{\mathbf{B}_{H}}_{\mathrm{c}}]_{\mathrm{b}} & = & \boldsymbol{\sigma}[{\mathbf{B}_{H}}_{\mathrm{c}}]_{\mathrm{b}} + \left(1 + \frac{\lVert \mathbf{B}_{\mathbf{U}}\rVert}{32}\right)R_{\mathrm{block}} \\
\qquad\forall_{\mathbf{U} \in \mathbf{B}_{\mathbf{U}}}: \\ \nonumber
\boldsymbol{\sigma}'[\mathbf{U}_{\mathrm{c}}] & = & \begin{cases}
\varnothing &\text{if}\ \boldsymbol{\sigma}[\mathbf{U}_{\mathrm{c}}] = \varnothing\ \wedge\ R = 0 \\
\mathbf{a}' &\text{otherwise}
\end{cases} \\
\mathbf{a}' &\equiv& (\boldsymbol{\sigma}[U_{\mathrm{c}}]_{\mathrm{n}}, \boldsymbol{\sigma}[U_{\mathrm{c}}]_{\mathrm{b}} + R, \boldsymbol{\sigma}[U_{\mathrm{c}}]_{\mathbf{s}}, \boldsymbol{\sigma}[U_{\mathrm{c}}]_{\mathrm{c}}) \\
R & \equiv & \left(1 + \frac{1}{8} (U_{\mathrm{i}} - {B_{H}}_{\mathrm{i}})\right) R_{\mathrm{block}}
\end{eqnarray}

@@

\begin{eqnarray}
\Xi_{\mathtt{EXPMOD}} &\equiv& \Xi_{\mathtt{PRE}} \quad \text{except:} \\
g_{\mathrm{r}} &=& \left\lfloor\frac{f\big(\max(\ell_{M},\ell_{B})\big)\max(\ell'_{E},1)}{G_{quaddivisor}}\right\rfloor \\
f(x) &\equiv& \begin{cases}
x^2 & \text{if}\ x \le 64 \\[0.5em]
\left\lfloor\dfrac{x^2}{4}\right\rfloor + 96 x - 3072 & \text{if}\ 64 < x \le 1024 \\[1em]
\left\lfloor\dfrac{x^2}{16}\right\rfloor + 480x - 199680 & \text{otherwise}
\end{cases}\\
\ell'_{E} &=& \begin{cases}
0 & \text{if}\ \ell_{E}\le 32\wedge E=0 \\
\lfloor \log_2(E)\rfloor &\text{if}\ \ell_{E}\le 32 \wedge E \neq 0 \\
8(\ell_{E} - 32) + \lfloor \log_2(i[(96+\ell_{B})..(127+\ell_{B})]) \rfloor & \text{if}\ 32 < \ell_{E} \wedge i[(96 + \ell_{B})..(127 + \ell_{B})]\neq 0 \\
8(\ell_{E} - 32) & \text{otherwise} \\
\end{cases} \\
\mathbf o &=& \left(B^E\bmod M\right)\in\mathbb P_{8\ell_{M}} \\
\ell_{B} &\equiv& i[0..31] \\
\ell_{E} &\equiv& i[32..63] \\
\ell_{M} &\equiv& i[64..95] \\
B &\equiv& i[96..(95+\ell_{B})] \\
E &\equiv& i[(96+\ell_{B})..(95+\ell_{B}+\ell_{E})] \\
M &\equiv& i[(96+\ell_{B}+\ell_{E})..(95+\ell_{B}+\ell_{E}+\ell_{M})] \\
i[x] &\equiv& \begin{cases}
I_{\mathbf d}[x] &\text{if}\ x < |I_{\mathbf d}| \\
0 &\text{otherwise}
\end{cases}
\end{eqnarray}

@@

We define $\Xi_{\mathtt{SNARKV}}$ as a precompiled contract for zkSNARK verification.
\begin{eqnarray}
\Xi_{\mathtt{SNARKV}}&\equiv&\Xi_{\mathtt{PRE}}\quad\text{except:}\\
\qquad\Xi_{\mathtt{SNARKV}}(\boldsymbol\sigma,g,I)&=&\left(\varnothing,0,A^0,()\right)\quad\text{if}\ F\\
F&\equiv&(|I_{\mathbf{d}}|\bmod 192\neq 0\vee(\exists j.\ a_{\mathrm{j}}=\varnothing\vee b_{\mathrm{j}}=\varnothing))\\
k &=& \dfrac{|I_{\mathbf{d}}|}{192} \\
g_{\mathrm{r}}&=& 60000k + 40000 \\
\mathbf o[0..31]&\equiv&\begin{cases}
0x0000000000000000000000000000000000000000000000000000000000000001&\text{if}\ v\wedge\neg F\\
0x0000000000000000000000000000000000000000000000000000000000000000&\text{if}\ \neg v\wedge\neg F
\end{cases}\\
v&\equiv&(\log_{P_1}(a_1)\times\log_{P_2}(b_1)+\cdots+\log_{P_1}(a_{\mathrm{k}})\times\log_{P_2}(b_{\mathrm{k}})\equiv 1\mod q)\\
a_1&\equiv&\delta_1(I_{\mathbf d}[0..63])\\
b_1&\equiv&\delta_2(I_{\mathbf d}[64..191])\\\nonumber
\vdots\\
a_{\mathrm{k}}&\equiv&\delta_1(I_{\mathbf d}[(|I_{\mathbf d}|-192)..(|I_{\mathbf d}|-129)])\\
b_{\mathrm{k}}&\equiv&\delta_2(I_{\mathbf d}[(|I_{\mathbf d}|-128)..(|I_{\mathbf d}|-1)])
\end{eqnarray}

@@

\begin{eqnarray}
\Xi_{\mathtt{BN\_ADD}}&\equiv&\Xi_{\mathtt{BN\_PRE}}\quad\text{except:}\\
\Xi_{\mathtt{BN\_ADD}}(\boldsymbol\sigma,g,I)&=&\left(\varnothing,0,A^0,()\right)\quad\text{if}\ x=\varnothing\vee y=\varnothing\\
g_{\mathrm{r}} &=& 500\\
\mathbf o&\equiv&\delta_1^{-1}(x+y)\quad\text{where $+$ is the group operation in $G_1$}\\
x&\equiv&\delta_1\left(\bar I_{\mathbf d}[0..63]\right)\\
y&\equiv&\delta_1\left(\bar I_{\mathbf d}[64..127]\right)\\
\label{eq:complemented_input}\bar I_{\mathbf d}[x]&\equiv&\begin{cases}
I_{\mathbf d}[x]&\text{if}\ x < |I_{\mathbf d}|\\
0&\text{otherwise}
\end{cases}
\end{eqnarray}

We define a precompiled contract for scalar multiplication on $G_1$, where $\bar I_{\mathbf d}$ is defined in (\ref{eq:complemented_input}).
\begin{eqnarray}
\Xi_{\mathtt{BN\_MUL}}&\equiv&\Xi_{\mathtt{PRE}}\quad\text{except:}\\
\Xi_{\mathtt{BN\_MUL}}(\boldsymbol\sigma,g,I)&=&\left(\varnothing,0,A^0,()\right)\quad\text{if}\ x=\varnothing\\
g_{\mathrm{r}} &=& 40000\\
\mathbf o&\equiv&\delta_1^{-1}(n\cdot x)\quad\text{where $\cdot$ is the scalar multiplication in $G_1$}\\
n&\equiv&\bar I_{\mathbf d}[0..31]\\
x&\equiv&\delta_1\left(\bar I_{\mathbf d}[32..95]\right)
\end{eqnarray}

@@

where:
\begin{equation}
C_{mem}(a) \equiv G_{memory} \cdot a + \left\lfloor \dfrac{a^2}{512} \right\rfloor
\end{equation}

>>>>

After the message call or contract creation is processed, the state is finalised by determining the amount to be refunded, $g^*$ from the remaining gas, $g'$, plus some allowance from the refund counter, to the sender at the original rate.
\begin{equation}
g^* \equiv g' + \min \{ \Big\lfloor \dfrac{T_{\mathrm{g}} - g'}{2} \Big\rfloor, \hyperlink{refund_balance_defn_words_A__r}{A_{\mathrm{r}}} \}
\end{equation}

@@

Throughout the present work, it is assumed that if $\boldsymbol{\sigma}_1[r]$ was originally undefined, it will be created as an account with no code or state and zero balance and nonce. Thus the previous equation should be taken to mean:
\begin{equation}
\boldsymbol{\sigma}_1 \equiv \boldsymbol{\sigma}_1' \quad \text{except:} \\
\end{equation}
\begin{equation}
\boldsymbol{\sigma}_1[s] \equiv \begin{cases}
\varnothing & \text{if}\ \boldsymbol{\sigma}_1'[s] = \varnothing \ \wedge\ v = 0 \\
\mathbf{a}_1 &\text{otherwise}
\end{cases}
\end{equation}
\begin{equation}
\mathbf{a}_1 \equiv (\boldsymbol{\sigma}_1'[s]_{\mathrm{n}}, \boldsymbol{\sigma}_1'[s]_{\mathrm{b}} - v, \boldsymbol{\sigma}_1'[s]_{\mathbf{s}}, \boldsymbol{\sigma}_1'[s]_{\mathrm{c}})
\end{equation}
\begin{equation}
\text{and}\quad \boldsymbol{\sigma}_1' \equiv \boldsymbol{\sigma} \quad \text{except:} \\
\end{equation}
\begin{equation}
\begin{cases}
\boldsymbol{\sigma}_1'[r] \equiv (0, v, \mathtt{\tiny TRIE}(\varnothing), \mathtt{\tiny KEC}(())) & \text{if} \quad \boldsymbol{\sigma}[r] = \varnothing \wedge v \neq 0 \\
\boldsymbol{\sigma}_1'[r] \equiv \varnothing & \text{if}\quad \boldsymbol{\sigma}[r] = \varnothing \wedge v = 0 \\
\boldsymbol{\sigma}_1'[r] \equiv \mathbf{a}_1' & \text{otherwise}
\end{cases}
\end{equation}
\begin{equation}
\mathbf{a}_1' \equiv (\boldsymbol{\sigma}[r]_{\mathrm{n}}, \boldsymbol{\sigma}[r]_{\mathrm{b}} + v, \boldsymbol{\sigma}[r]_{\mathbf{s}}, \boldsymbol{\sigma}[r]_{\mathrm{c}})
\end{equation}

@@

The application of rewards to a block involves raising the balance of the accounts of the beneficiary address of the block and each ommer by a certain amount. We raise the block's beneficiary account by \hyperlink{R__block}{$R_{\mathrm{block}}$}; for each ommer, we raise the block's beneficiary by an additional $\frac{1}{32}$ of the block reward and the beneficiary of the ommer gets rewarded depending on the block number.\hypertarget{Omega}{} Formally we define the function $\Omega$:
\begin{eqnarray}
\\ \nonumber
\Omega(B, \boldsymbol{\sigma}) & \equiv & \boldsymbol{\sigma}': \boldsymbol{\sigma}' = \boldsymbol{\sigma} \quad \text{except:} \\
\qquad\boldsymbol{\sigma}'[{\mathbf{B}_{H}}_{\mathrm{c}}]_{\mathrm{b}} & = & \boldsymbol{\sigma}[{\mathbf{B}_{H}}_{\mathrm{c}}]_{\mathrm{b}} + (1 + \frac{\lVert \mathbf{B}_{\mathbf{U}}\rVert}{32})R_{\mathrm{block}} \\
\qquad\forall_{\mathbf{U} \in \mathbf{B}_{\mathbf{U}}}: \\ \nonumber
\boldsymbol{\sigma}'[\mathbf{U}_{\mathrm{c}}] & = & \begin{cases}
\varnothing &\text{if}\ \boldsymbol{\sigma}[\mathbf{U}_{\mathrm{c}}] = \varnothing\ \wedge\ R = 0 \\
\mathbf{a}' &\text{otherwise}
\end{cases} \\
\mathbf{a}' &\equiv& (\boldsymbol{\sigma}[U_{\mathrm{c}}]_{\mathrm{n}}, \boldsymbol{\sigma}[U_{\mathrm{c}}]_{\mathrm{b}} + R, \boldsymbol{\sigma}[U_{\mathrm{c}}]_{\mathbf{s}}, \boldsymbol{\sigma}[U_{\mathrm{c}}]_{\mathrm{c}}) \\
R & \equiv & (1 + \frac{1}{8} (U_{\mathrm{i}} - {B_{H}}_{\mathrm{i}})) R_{\mathrm{block}}
\end{eqnarray}

@@

\begin{eqnarray}
\Xi_{\mathtt{EXPMOD}} &\equiv& \Xi_{\mathtt{PRE}} \quad \text{except:} \\
g_{\mathrm{r}} &=& \Big\lfloor\frac{f\big(\max(\ell_{M},\ell_{B})\big)\max(\ell'_{E},1)}{G_{quaddivisor}}\Big\rfloor \\
f(x) &\equiv& \begin{cases}
x^2 & \text{if}\ x \le 64 \\
\Big\lfloor\dfrac{x^2}{4}\Big\rfloor + 96 x - 3072 & \text{if}\ 64 < x \le 1024 \\
\Big\lfloor\dfrac{x^2}{16}\Big\rfloor + 480x - 199680 & \text{otherwise}
\end{cases}\\
\ell'_{E} &=& \begin{cases}
0 & \text{if}\ \ell_{E}\le 32\wedge E=0 \\
\lfloor \log_2(E)\rfloor &\text{if}\ \ell_{E}\le 32 \wedge E \neq 0 \\
8(\ell_{E} - 32) + \lfloor \log_2(i[(96+\ell_{B})..(127+\ell_{B})]) \rfloor & \text{if}\ 32 < \ell_{E} \wedge i[(96 + \ell_{B})..(127 + \ell_{B})]\neq 0 \\
8(\ell_{E} - 32) & \text{otherwise} \\
\end{cases} \\
\mathbf o &=& (B^E\bmod M)\in\mathbb P_{8\ell_{M}} \\
\ell_{B} &\equiv& i[0..31] \\
\ell_{E} &\equiv& i[32..63] \\
\ell_{M} &\equiv& i[64..95] \\
B &\equiv& i[96..(95+\ell_{B})] \\
E &\equiv& i[(96+\ell_{B})..(95+\ell_{B}+\ell_{E})] \\
M &\equiv& i[(96+\ell_{B}+\ell_{E})..(95+\ell_{B}+\ell_{E}+\ell_{M})] \\
i[x] &\equiv& \begin{cases}
I_{\mathbf d}[x] &\text{if}\ x < |I_{\mathbf d}| \\
0 &\text{otherwise}
\end{cases}
\end{eqnarray}

@@

We define $\Xi_{\mathtt{SNARKV}}$ as a precompiled contract for zkSNARK verification.
\begin{eqnarray}
\Xi_{\mathtt{SNARKV}}&\equiv&\Xi_{\mathtt{PRE}}\quad\text{except:}\\
\qquad\Xi_{\mathtt{SNARKV}}(\boldsymbol\sigma,g,I)&=&(\varnothing,0,A^0,())\quad\text{if}\ F\\
F&\equiv&(|I_{\mathbf{d}}|\bmod 192\neq 0\vee(\exists j.\ a_{\mathrm{j}}=\varnothing\vee b_{\mathrm{j}}=\varnothing))\\
k &=& \dfrac{|I_{\mathbf{d}}|}{192} \\
g_{\mathrm{r}}&=& 60000k + 40000 \\
\mathbf o[0..31]&\equiv&\begin{cases}
0x0000000000000000000000000000000000000000000000000000000000000001&\text{if}\ v\wedge\neg F\\
0x0000000000000000000000000000000000000000000000000000000000000000&\text{if}\ \neg v\wedge\neg F
\end{cases}\\
v&\equiv&(\log_{P_1}(a_1)\times\log_{P_2}(b_1)+\cdots+\log_{P_1}(a_{\mathrm{k}})\times\log_{P_2}(b_{\mathrm{k}})\equiv 1\mod q)\\
a_1&\equiv&\delta_1(I_{\mathbf d}[0..63])\\
b_1&\equiv&\delta_2(I_{\mathbf d}[64..191])\\\nonumber
\vdots\\
a_{\mathrm{k}}&\equiv&\delta_1(I_{\mathbf d}[(|I_{\mathbf d}|-192)..(|I_{\mathbf d}|-129)])\\
b_{\mathrm{k}}&\equiv&\delta_2(I_{\mathbf d}[(|I_{\mathbf d}|-128)..(|I_{\mathbf d}|-1)])
\end{eqnarray}

@@

\begin{eqnarray}
\Xi_{\mathtt{BN\_ADD}}&\equiv&\Xi_{\mathtt{BN\_PRE}}\quad\text{except:}\\
\Xi_{\mathtt{BN\_ADD}}(\boldsymbol\sigma,g,I)&=&(\varnothing,0,A^0,())\quad\text{if}\ x=\varnothing\vee y=\varnothing\\
g_{\mathrm{r}} &=& 500\\
\mathbf o&\equiv&\delta_1^{-1}(x+y)\quad\text{where $+$ is the group operation in $G_1$}\\
x&\equiv&\delta_1(\bar I_{\mathbf d}[0..63])\\
y&\equiv&\delta_1(\bar I_{\mathbf d}[64..127])\\
\label{eq:complemented_input}\bar I_{\mathbf d}[x]&\equiv&\begin{cases}
I_{\mathbf d}[x]&\text{if}\ x < |I_{\mathbf d}|\\
0&\text{otherwise}
\end{cases}
\end{eqnarray}

We define a precompiled contract for scalar multiplication on $G_1$, where $\bar I_{\mathbf d}$ is defined in (\ref{eq:complemented_input}).
\begin{eqnarray}
\Xi_{\mathtt{BN\_MUL}}&\equiv&\Xi_{\mathtt{PRE}}\quad\text{except:}\\
\Xi_{\mathtt{BN\_MUL}}(\boldsymbol\sigma,g,I)&=&(\varnothing,0,A^0,())\quad\text{if}\ x=\varnothing\\
g_{\mathrm{r}} &=& 40000\\
\mathbf o&\equiv&\delta_1^{-1}(n\cdot x)\quad\text{where $\cdot$ is the scalar multiplication in $G_1$}\\
n&\equiv&\bar I_{\mathbf d}[0..31]\\
x&\equiv&\delta_1(\bar I_{\mathbf d}[32..95])
\end{eqnarray}

@@

where:
\begin{equation}
C_{mem}(a) \equiv G_{memory} \cdot a + \Big\lfloor \dfrac{a^2}{512} \Big\rfloor
\end{equation}
